Update Meeting: 14-06-2021

### 2021-07-22 analysis/update_meeting_14_06_2021.Rmd
wflow_publish("analysis/update_meeting_14_06_2021.Rmd")

```{r, echo=FALSE,include = FALSE}
# You need this code to conduct the magic dependences attaching...
DT::datatable(matrix())
```

@@

```{r traits, echo = FALSE}

@@

```{r sex_het, echo = FALSE}

@@

```{r mr_summary_age, echo = FALSE}

>>>>

```{r, echo=FALSE,include = FALSE}
# You need this code to conduct the magic dependencies attaching...
DT::datatable(matrix())
```

@@

```{r traits, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}

@@

```{r sex_het, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}

@@

```{r mr_summary_age, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}
